Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-10 documentation/paper.tex
Filled in table without wall cuts
Described tables

This chart shows that simple network architectures seem to produce better accuracy, likely due to reduced overfitting. Larger kernel sizes, more filters, and more layers make performance generally worse, while higher L2 regularization does the opposite. Dropout seems to have a weak correlation, possibly reducing accuracy slightly.

@@

\begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Configuration & L2 $\lambda$ & Dropout & Layers & Max Accuracy & Class-Wise Std Dev \\
    \hline
    $FourierMLP(PosCor(\beta_{8}))$ & 0 & 0.5 & 2 & 95\% & 0.56 \\
    \hline
    $FourierMLP(\beta_{8})$ & 0 & 0.5 & 2 & 98\% & 0.29 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.5 & 3 & 95\% & 0.44 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.25 & 3 & 97\% & 0.43 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 0.003 & 0.25 & 3 & 93\% & 0.54 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 94\% & 0.52 \\
    \hline
\end{tabular}

@@

>>>>

This table shows that simple network architectures seem to produce better accuracy, likely due to reduced overfitting. Larger kernel sizes, more filters, and more layers make performance generally worse, while higher L2 regularization does the opposite. Dropout seems to have a weak correlation, possibly reducing accuracy slightly.

@@

\begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Configuration & L2 $\lambda$ & Dropout & Layers & Max Accuracy & Class-Wise Std Dev \\
    \hline
    $FourierMLP(PosCor(\beta_{8}))$ & 0 & 0.5 & 2 & 95\% & 0.56 \\
    \hline
    $FourierMLP(\beta_{8})$ & 0 & 0.5 & 2 & 98\% & 0.29 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.5 & 3 & 95\% & 0.44 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.25 & 3 & 97\% & 0.43 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 0.003 & 0.25 & 3 & 93\% & 0.54 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 94\% & 0.52 \\
    \hline
    $FourierMLPWithPos(\beta_{40}, \chi)$ & 0 & 0 & 3 & 91\% & 0.57 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.0003 & 0 & 4 & 91\% & 0.53 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.25 & 4 & 91\% & 0.56 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.5 & 3 & 89\% & 0.64 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.5 & 4 & 89\% & 0.65 \\
    \hline
\end{tabular}

It is very clear here that higher resolutions do not improve accuracy. Regularization, both dropout and L2, appears to have relatively little effect.

@@

\begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Configuration & L2 $\lambda$ & Dropout & Layers & Max Accuracy & Class-Wise Std Dev \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 92\% & 0.63 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0 & 0 & 3 & 95\% & 0.49 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0 & 2 & 96\% & 0.47 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0 & 2 & 97\% & 0.47 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.25 & 2 & 95\% & 0.54 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.5 & 2 & 94\% & 0.53 \\
    \hline
\end{tabular}

Without wall cuts, the full-resolution Fourier transform produces much more effective discriminators. Here, L2 regularization is beneficial, possibly because there is more noise that can be overfit on.
